---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ElasticIntegrative

<!-- badges: start -->
<!-- badges: end -->


## Overview

The goal of *ElasticIntegrative* is toimplement integrative analyses for the heterogenous treatment effect combining a randomized trial and a real-world evidence study.

Two datasets

* The randomized trial contains observations on (A,X,Y), where the treatment assignment A is randomized. 

* The real-world evidence study contains observations on (A,X,Y), where the treatment assignment A may be confounded.


## Installation with `devtools`:

```{r, eval = FALSE}
devtools::install_github("Gaochenyin/ElasticIntegrative")
library(ElasticIntegrative)
```

## Usage

This is an example for illustration
```{r example}
library(ElasticIntegrative)
## basic example code for data generation
set.seed(1234)
## setups
beta0 <- c(0, 1, 1, 1) # for the mu0 function
psi0 <- c(0, 1, 1) # for contrast function
n <- 1e5; mean.x <- 1 # the whole population
m <- 2000; tlocalpar <- 0 # size and bias for the RWE
# -------------------------------
## begin the data generation
X1.rt <- rnorm(n, mean.x, 1)
X2.rt <- rnorm(n, mean.x, 1)
X3.rt <- rnorm(n, mean.x, 1) 
X1.os <- rnorm(n, mean.x, 1)
X2.os <- rnorm(n, mean.x, 1)
X3.os <- rnorm(n, mean.x, 1) 
## construct functions
h.X.rt <- cbind(X1.rt, X2.rt, X3.rt)
h.X.os <- cbind(X1.os, X2.os, X3.os)
f.X.rt <- cbind(X1.rt, X2.rt)
f.X.os <- cbind(X1.os, X2.os)
# -------------------------------
## construct Y for RCT and RWE populations
### RCT population
Y0.rt <- cbind(1, h.X.rt) %*% beta0 + rnorm(n, 0, 1)
Y1.rt <- cbind(1, h.X.rt) %*% beta0 + cbind(1, f.X.rt) %*% psi0 + rnorm(n, 0, 1)
### RCT sample
eS <- exp(-4.5 - 2 * X1.rt - 2 * X2.rt)/
  (1 + exp(-4.5 - 2 * X1.rt - 2 * X2.rt))
S <- sapply(eS, rbinom, n = 1, size = 1)
S.ind <- which(S == 1)
n.t <- length(S.ind)
### choose the selected patients
X.rt <- f.X.rt[S.ind, ]
Y0.rt <- Y0.rt[S.ind]
Y1.rt <- Y1.rt[S.ind]
eS.rt <- eS[S.ind]
### assign treatment to trial participant with equal probabilities
ps.t <- rep(0.5, n.t)
A.rt <- rbinom(n.t, 1, ps.t)
Y.rt <- Y1.rt * A.rt + Y0.rt * (1 - A.rt)
# -------------------------------
### RWE population
Y0.os <- cbind(1, h.X.os) %*% beta0 + rnorm(n, 0, 1)
Y1.os <- cbind(1, h.X.os) %*% beta0 + cbind(1, f.X.os) %*% psi0 + rnorm(n, 0, 1)
### OS sample
P.ind <- sample(1:n, size = m)
X.os <- f.X.os[P.ind, ]
X.confounder.os <- X3.os[P.ind]
Y0.os <- Y0.os[P.ind]
Y1.os <- Y1.os[P.ind]
# 0.058 is chosen to maintain the proportion of the treated at about .5
eA <- exp(0.058 - 1 * X.os[, 1] + 1 * X.os[, 2] - tlocalpar * X.confounder.os)/
  {1+exp(0.058 - 1 * X.os[, 1] + 1 * X.os[, 2] - tlocalpar * X.confounder.os)}
A.os <- sapply(eA, rbinom, n = 1, size = 1)
Y.os <- Y1.os * A.os + Y0.os * (1 - A.os)
# sort the RT and RW datasets
dat.t <- list(
  Y = Y.rt, A = A.rt, X = X.rt, q = rep(1, n.t),
  ps = ps.t,
  ml.ps = ps.t
)
dat.os <- list(Y = Y.os, A = A.os, X = X.os, q = rep(1, m))
# begin the elastic integrative analysis
# choice of kappa_n, default is tau = 1 (similar to BIC criteria)
tau <- 1
result.elastic <- elasticHTE(dat.t = dat.t,
                             dat.os = dat.os,
                             thres.psi = tau * sqrt(log(m)), # threshold for ACI psi
                             fixed = FALSE)
```

## Value

 |
 --------------- | -------------
est | the HTE estimators including
i) `covj.t` |  the covariate adjustment estimator;
ii) `ee.rt(ml)`|  the RCT estimating equation estimator with sieve models;
iii) `opt.ee(ml)`| the RT&RW estimating equation estimator with sieve models;
iv) `elas`|  the elastic integrative estimator.
ve|   the bootstrap variance estimates for est.
CI |  $95\%$ percentiel bootstrap confidence intervals. Note `covj.t`, `ee.rt(ml)`, and `opt.ee(ml)` use the Wald CI and `elas` uses the adaptive  confidence with threshold `$\\sqrt(log(2000))$`.

```{r echo=FALSE}
# output the results
cat('est')
result.elastic$est[c(paste0('covj.t.',1:3),
                     paste0('ee.rt(ml).',1:3),
                     paste0('opt.ee(ml).',1:3),
                     paste0('elas.',1:3))]
cat('ve')
result.elastic$ve[c(paste0('covj.t.',1:3),
                    paste0('ee.rt(ml).',1:3),
                     paste0('opt.ee(ml).',1:3),
                     paste0('elas.',1:3))]
cat('CI')
cbind(lower = result.elastic$CIs.inf[c(paste0('covj.t.',1:3),
                                       paste0('ee.rt(ml).',1:3),
                                       paste0('opt.ee(ml).',1:3),
                                       paste0('elas.v2.',1:3))],
      upper = result.elastic$CIs.sup[c(paste0('covj.t.',1:3),
                                       paste0('ee.rt(ml).',1:3),
                     paste0('opt.ee(ml).',1:3),
                     paste0('elas.v2.',1:3))])


```

## More examples
```{r eval=FALSE, include=TRUE}
example(ElasticIntegrative::elasticHTE)
utils::browseVignettes("ElasticIntegrative")
```

