---
title: "Simulation example: comparing AIPW and SES"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation example: comparing AIPW and SES}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(ElasticIntegrative)
output_function <- function(x)
{
  bias <- (x$est[c(paste0('AIPW.', 2:3),
                     paste0('RT.', 2:3))]-1)
  ve <- x$ve[c(paste0('AIPW.', 2:3),
                     paste0('RT.', 2:3))]
  mse <- bias**2 + ve
  CP <- x$CP[c(paste0('AIPW.', 2:3),
                     paste0('RT.', 2:3))]
  width <- x$CI.width[c(paste0('AIPW.', 2:3),
                     paste0('RT.', 2:3))]
  rbind(bias = bias*100, S.D. = sqrt(ve)*1e3,
        'root-MSE' = sqrt(mse)*1e3, 'Coverage rate' = CP*1e2,
        width = width*1e3)
}
```
In this vignette, we will compare the performances of the AIPW-adjusted approach and the SES approach based on RT data (Yang et al., (2022), Section S4.1). The data generating mechanism is the same as in [here](sim_psi011_111.html) except
that we now consider different propensity score distributions. 

* (weak separation of propensity score distributions by treatment group) $\alpha = (-2,-1,-1)$.

* (median separation of propensity score distributions by treatment group) $\alpha = (-2,-2,-2)$.

* (strong separation of propensity score distributions by treatment group) $\alpha = (-2,-3,-3)$.

The following figure shows the propensity score distributions by treatment group and demonstrates the degrees of separation in the three scenarios. 
```{r ps_dist, echo = TRUE, echo=FALSE, fig.height=5, fig.width=6.5, fig.align = 'center'}
# treatment plot
set.seed(1)
mean.x <- 1;n <- 1e5
# change mean to 1; intercept
X1 <- rnorm(n, mean.x, 1); X2 <- rnorm(n, mean.x, 1);
f.X <- cbind(X1, X2)
# true ATE
eS <- exp(-4.5 -2 * X1 -2 *  X2)/{1+exp(-4.5 -2 * X1 -2 *  X2)}
S <- sapply(eS,rbinom,n = 1, size = 1)
S.ind <- which(S==1)
X.t <- f.X[S.ind,]
n.t <- length(S.ind)
# need to change to produce for weight = -2
ps.t.1 <- exp(-2+X.t%*%c(-1,-1))/{1+exp(-2+X.t%*%c(-1,-1))}
ps.t.2 <- exp(-2+X.t%*%c(-2,-2))/{1+exp(-2+X.t%*%c(-2,-2))}
ps.t.3 <- exp(-2+X.t%*%c(-3,-3))/{1+exp(-2+X.t%*%c(-3,-3))}
A.t.1  <- rbinom(n.t,1,ps.t.1)
A.t.2  <- rbinom(n.t,1,ps.t.2)
A.t.3  <- rbinom(n.t,1,ps.t.3)

ps.mat <- cbind(c(ps.t.1, ps.t.2, ps.t.3),
      c(A.t.1, A.t.2, A.t.3),
      c(rep(1, n.t),
        rep(2, n.t),
        rep(3, n.t)))

xy.labs <- c('Weak',
             'Median',
             'Strong')
names(xy.labs) <- 1:3

ggplot(data = data.frame(ps.mat),
       aes(x = X1, fill = as.factor(X2)))+
  geom_density(alpha = 0.5)+
  facet_wrap(~X3, scales = "free",
             labeller =as_labeller(xy.labs))+
  theme(legend.position = 'top')+
  theme(axis.text = element_text(size = 10),
        text = element_text(size = 12),
        legend.text=element_text(size=12))+
  theme(plot.margin=unit(c(0.3,0.3,0,0),"cm"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))+
  scale_fill_discrete(name = 'A')+xlab('')
```

The simulation results (Yang et al., (2022), Table S2) for comparing RT.AIPW and RT.SES are the following:
```{r echo=FALSE}
# check data-raw/DATASET_AIPW.R for details of data generation
summary.res.l1 <- summary(elastic_aipw_ses_l1_list,
                                   psi = c(0,1,1))
summary.res.l2 <- summary(elastic_aipw_ses_l2_list,
                                   psi = c(0,1,1))
summary.res.l3 <- summary(elastic_aipw_ses_l3_list,
                                   psi = c(0,1,1))
# summarize the results
tab.l1 <- output_function(summary.res.l1)
tab.l2 <- output_function(summary.res.l2)
tab.l3 <- output_function(summary.res.l3)
# output
knitr::kable(tab.l1, digits = 1,
             caption = 'Case 1: weak separation')%>%
  kableExtra::kable_styling(full_width = FALSE, position = "float_left")
knitr::kable(tab.l2, digits = 1,
             caption = 'Case 2: median separation')%>%
  kableExtra::kable_styling(full_width = FALSE, position = "float_left")
knitr::kable(tab.l3, digits = 1,
             caption = 'Case 3: strong separation')%>%
  kableExtra::kable_styling(full_width = FALSE, position = "float_left")
```
